\begin{thebibliography}{0}
    \bibitem{age1994}\hypertarget{age1994}{}
    \href{https://pdfs.semanticscholar.org/20cb/d360c8e6f70aac3e11853d81e3b18e4866c2.pdf}
    {Age Classification from Facial Images.
    Young H. Kwon, Niels da Vitoria Lobo.
    In IEEE 1994}

    \bibitem{unfiltered}\hypertarget{unfiltered}{}
    \href{https://www.openu.ac.il/home/hassner/Adience/EidingerEnbarHassner_tifs.pdf}
    {Age and Gender Estimation of Unfiltered Faces.
    Eran Eidinger, Roee Enbar, Tal Hassner.
    In IEEE 2014}

    \bibitem{hassner}\hypertarget{hassner}{}
    \href{https://talhassner.github.io/home/projects/cnn_agegender/CVPR2015_CNN_AgeGenderEstimation.pdf}
    {Age and Gender Classification using Convolutional Neural Networks.
    Gil Levi, Tal Hassner.
    In IEEE 2015}

    \bibitem{INDIA}\hypertarget{INDIA}{}
    \href{https://ieeexplore.ieee.org/document/8282221}
    {Age/gender classification with whole-component convolutional neural networks (WC-CNN).
    Chun-Ting Huang, Yueru Chen, Ruiyuan Lin, C.-C. Jay Kuo.
    In IEEE 2018}

    \bibitem{smoll}\hypertarget{smoll}{}
    \href{https://merl.com/publications/docs/TR2002-12.pdf}
    {Learning Gender with Support Faces.
    Baback Moghaddam, Ming-Hsuan Yang.
    In IEEE 2002}

    \bibitem{lbp_age}\hypertarget{lbp_age}{}
    \href{https://link.springer.com/chapter/10.1007/978-3-540-74549-5_49}
    {Demographic Classification with Local Binary Patterns.
    Zhiguang Yang, Haizhou Ai. In ICB 2007}

    \bibitem{face_detection}\hypertarget{face_detection}{}
    \href{http://www.face-rec.org/algorithms/Boosting-Ensemble/16981346.pdf}
    {Robust Real-Time Face Detection.
    Paul Viola, Michael J. Jones.
    In IEEE 2003}

    \bibitem{face_detection2}\hypertarget{face_detection2}{}
    \href{http://rodrigob.github.io/documents/2014_eccv_face_detection_with_supplementary_material.pdf}
    {Face detection without bells and whistles.
    Makrus Mathias, Rodrigo Beneson, Marco Pedersoli, Lus Van Gool.
    In ECCV 2014}

    \bibitem{face_detection3}\hypertarget{face_detection3}{}
    \href{https://arxiv.org/abs/1905.01585}
    {Accurate Face Detection for High Performance.
    Faen Zhang, Xinyu Fan, Guo Ai, Jianfei Song, Yongqiang Qin, Jiahong Wu. In ArXiv 2019}

    \bibitem{resnet}\hypertarget{resnet}{}
    \href{https://arxiv.org/abs/1512.03385}
    {Deep Residual Learning for Image Recognition.
    Kaiming He, Xiangyu Zhang, Shaoqing Ren, Jian Sun.
    In IEEE 2015}

    \bibitem{retinaface}\hypertarget{retinaface}{}
    \href{https://arxiv.org/abs/1905.00641}
    {RetinaFace: Single-stage Dense Face Localisation in the Wild.
    Jiankang Deng, Jia Guo, Yuxiang Zhou, Jinke Yu, Irene Kotsia, Stefanos Zafeiriou.
    In ArXiv 2019
    }

    \bibitem{align}\hypertarget{align}{}
    \href{http://www.csc.kth.se/~vahidk/papers/KazemiCVPR14.pdf}
    {One Millisecond Face Alignment with an Ensemble of Regression Trees.
    Vahid Kazemi and Josephine Sullivan.
    In IEEE 2014}

    \bibitem{lbp}\hypertarget{lpb}{}
    \href{https://arxiv.org/abs/1511.06316}
    {Face Anti-Spoofing Based on Color Texture Analysis.
    Zinelabidine Boulkenafet, Jukka Komulainen, Abdenour Hadid.
    In IEEE 2015}

    \bibitem{lbp2}\hypertarget{lpb2}{}
    \href{https://arxiv.org/abs/1803.11097}
    {Learning Deep Models for Face Anti-Spoofing: Binary or Auxiliary Supervision.
    Yaojie Liu, Amin Jourabloo, Xiaoming Liu.
    In IEEE/CVF 2018}

    \bibitem{lbp3}\hypertarget{lpb3}{}
    \href{https://arxiv.org/abs/1904.02860}
    {Deep Tree Learning for Zero-shot Face Anti-Spoofing.
    Yaojie Liu, Joel Stehouwer, Amin Jourabloo, Xiaoming Liu.
    In IEEE/CVF 2019}

    \bibitem{pfid}\hypertarget{pfid}{}
    \href{https://arxiv.org/abs/1907.02642}
    {Primate Face Identification in the Wild.
    Ankita Shukla, Gullal Singh Cheema, Saket Anand, Qamar Qureshi, Yadvendradev Jhala.
    In PRICAI 2019}

    \bibitem{pfid2}\hypertarget{pfid2}{}
    \href{https://arxiv.org/abs/1406.4773}
    {Deep Learning Face Representation by Joint Identification-Verification.
    Yi Sun, Xiaogang Wang, Xiaoou Tang.
    In NIPS 2014}

    \bibitem{pfid3}\hypertarget{pfid3}{}
    \href{https://ydwen.github.io/papers/WenECCV16.pdf}
    {A Discriminative Feature Learning Approach for Deep Face Recognition.
    Yandong Wen, Kaipeng Zhang, Zhifeng Li, and Yu Qiao.
    In ECCV 2016}

    \bibitem{densenet}\hypertarget{densenet}{}
    \href{https://arxiv.org/abs/1608.06993}
    {Densely Connected Convolutional Networks.
    Gao Huang, Zhuang Liu, Laurens van der Maaten, Kilian Q. Weinberger.
    In IEEE 2016}

    \bibitem{NUAA}\hypertarget{NUAA}{}
    \href{http://parnec.nuaa.edu.cn/xtan/data/nuaaimposterdb.html}
    {NUAA Photograph Imposter Database}

    \bibitem{lfw}\hypertarget{lfw}{}
    \href{http://vis-www.cs.umass.edu/lfw/}
    {Labeled Faces in the Wild Database}

    \bibitem{IMDB-WIKI}\hypertarget{IMDB-WIKI}{}
    \href{https://data.vision.ee.ethz.ch/cvl/rrothe/imdb-wiki/}
    {IMDB-WIKI Database}

    \bibitem{bug}\hypertarget{bug}{}
    \href{https://ibug.doc.ic.ac.uk/resources/300-W/}
    {300 Faces In-the-Wild Database}

    \bibitem{DEEP}\hypertarget{DEEP}{}
    \href{https://arxiv.org/pdf/1710.02985.pdf}
    {Age Group and Gender Estimation in the Wild with Deep RoR Architecture.
    Ke Zhang, Ce Gao, Liru Guo, Miao Sun, Xingfang Yuan, Tony X. Han, Zhenbing Zhao and Baogang Li.
    In IEEE 2017
    }

    \bibitem{LRN}\hypertarget{LRN}{}
    \href{https://papers.nips.cc/paper/4824-imagenet-classification-with-deep-convolutional-neural-networks.pdf}
    {ImageNet Classification with Deep Convolutional Neural Networks.
    Alex Krizhevsky, Ilya Sutskever, Geoffrey E. Hinton.
    In Advances in neural information processing systems 2012
    }

    \bibitem{imdb}\hypertarget{imdb}{}
    \href{https://data.vision.ee.ethz.ch/cvl/publications/papers/proceedings/eth_biwi_01229.pdf}
    {DEX: Deep EXpectation of apparent age from a single image.
    Rasmus Rothe, Radu Timofte, Luc Van Gool.
    In IJCV 2016
    }

    \bibitem{LAP}\hypertarget{LAP}{}
    \href{http://refbase.cvc.uab.es/files/EFP2015.pdf}
    {
        Sergio Escalera, Junior Fabian, Pablo Pardo, Xavier Baro, Jordi Gonzalez, Hugo J. Escalante, Marc Oliu, Dusan Misevic, Ulrich Steiner, Isabelle Guyon.
        In EFP 2015.
    }
\end{thebibliography}